---
title: "QMM_Assignment_02"
author: "Tanmaiyee"
date: "2024-09-21"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1. The Weigelt Corporation has three branch plants with excess production capacity. Fortunately,the corporation has a new product ready to begin production, and all three plants have this capability, so some of the excess capacity can be used in this way. This product can be made in three sizes--large, medium, and small--that yield a net unit profit of $420, $360, and $300, respectively. Plants 1, 2, and 3 have the excess capacity to produce 750, 900, and 450 units per day of this product, respectively, regardless of the size or combination of sizes involved. The amount of available in-process storage space also imposes a limitation on the production rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000 square feet, respectively, of in-process storage space available for a day's production of this product. Each unit of the large, medium, and small sizes produced per day requires 20, 15, and 12 square feet,respectively. Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large, medium, and small sizes, respectively, would be sold per day. At each plant, some employees will need to be laid off unless most of the plant’s excess production capacity can be used to produce the new product. To avoid layoffs if possible, management has decided that the plants should use the same percentage of their excess capacity to produce the new product.Management wishes to know how much of each of the sizes should be produced by each of the plants to maximize profit. Solve the problem using lpsolve, or any other equivalent library in R

***

The below two packages provide functions for linear programming. Under this assignment, a ".lp" file was created with the objective function and the constraints which is then used in R programming to get the desired output.

The required libraries are installed and the data is set to read from the ".lp" file. The data is then stored in a variable called "x"

```{r}
library(lpSolve)
library(lpSolveAPI)
WC_data <- read.lp("xyz.lp")
```


```{r}
# To find the solution that maximizes the objective function
solve(WC_data)
# To achieve max profit
get.objective(WC_data)
# To get values of decision variables to achieve optimal solution
get.variables(WC_data)   
# To get right hand constraints values
get.constraints(WC_data)
```
```{r}
# Optimum production strategy for each plant

production <- data.frame(
  Plant = c("Plant 1", "Plant 2", "Plant 3"),
  Large = c(0, 500, 250),
  Medium = c(666.66, 400, 133.33),
  Small = c(83.33, 0, 0)
)

print(production)
```

***

Results:

From the above results we can infer that, management can achieve max profit of 772000 provided the plants operate/produce in the following way:

Plant 1: It should produce 0 large units, 667 medium units and 83 small units.

Plant 2: It should produce 500 large units, 400 medium units and no small units

Plant 3: It should produce 250 large units, 133 medium units and no small units.
